Replacing {\tt H5Fis\_hdf5()} with {\tt H5Fis\_accessible()}

### 2014-07-30 RFCs/HDF5_Library/H5Fis_accessible/h5fis_accessible.tex
Former-commit-id: 11d6d77d1f8010905bbf9b2de2536b3266a3bd43

%% Abstract
\begin{abstract}
The HDF5 library provides a routine ({\tt H5Fis\_hdf5()}) to determine whether a given file is in the HDF5 format or not given the file name. This API routine is not robust however, and can be considered a bug in the API, because it only uses the default file driver when attempting to open the file. Furthermore, with the introduction of the HDF5 Virtual Object Layer (VOL), all HDF5 files that have not been created through the native HDF5 VOL plugin will not be in the HDF5 file format, but they are still accessible from the HDF5 library. We propose to address the two concerns outlined above by adding a new routine, {\tt H5Fis\_accessible()}, to eventually replace {\tt H5Fis\_hdf5()} in the HDF5 library.
\end{abstract}

@@

We decided to change the name of the function rather than fix the old function by adding the {\tt fapl\_id} argument for bacward compatibilty issues and the better representation of what the function does with the new name.

@@

%% References
%\bibliographystyle{ieeetr}
%\bibliography{}

>>>>

%% Abstract
\begin{abstract}
The HDF5 library provides a routine ({\tt H5Fis\_hdf5()}) to determine whether a given file is in the HDF5 format or not given the file name. This API routine is not robust however, and can be considered a bug in the API, because it only uses the default file driver when attempting to open the file. Furthermore, with the introduction of the HDF5 Virtual Object Layer (VOL)~\cite{vol-rfc}, all HDF5 files that have not been created through the native HDF5 VOL plugin will not be in the HDF5 file format, but they are still accessible from the HDF5 library. We propose to address the two concerns outlined above by adding a new routine, {\tt H5Fis\_accessible()}, to eventually replace {\tt H5Fis\_hdf5()} in the HDF5 library.
\end{abstract}

@@

We decided to change the name of the function rather than fix the old function by adding the {\tt fapl\_id} argument for backward compatibilty issues and the better representation of what the function does with the new name.

@@

%% References
\bibliographystyle{ieeetr}
\bibliography{h5fis_accessible}
